Appendix 1: sdmTMB statistical model description

### 2022-05-06 doc/appendix-model.Rmd
Update offset

Offset terms can be included with the reserved word `offset` in the formula.
E.g., `y ~ x + offset`.
These are included in the linear predictor as

@@

where $O_{\s,t}$ is an offset term---a **log transformed** variable without a coefficient (assuming a log link).

>>>>

Offset terms can be included through the `offset` argument in `sdmTMB()`.
These are included in the linear predictor as

@@

where $O_{\s,t}$ is an offset term---a **log transformed** variable without a coefficient (assuming a log link).
The offset is *not* included in the prediction.
Therefore, if `offset` represents a measure of effort, for example, the prediction is for one unit of effort (`log(1) = 0`).
